The limits of self commitment and private paternalism \thanks{}

### 2023-01-26 donde.tex
bounding censoring te & other results

We define a borrower's financial cost as the \textcolor{red}{outflow --in cash or pawn value-- from the borrower to the lender.} This includes all payments the borrower made toward interest and fees, but also the value of the pawn when there is default. When there is no default the borrower gets her pawn back and there is no loss of value for the borrower. Payments towards capital are considered a cost only when the borrower defaults, as she does not get reimbursed for these. Note however that when she does not default payments to capital are not an actual outflow, as they sum up to the value of the loan the lender disbursed in the first place. The formula for financial cost for person $i$ is thus as follows:

@@

\noindent where $t$ indexes days, and $\mathds{1}(\text{Default}_i)$ is an indicator function for defaulting. Even though we observe transactions at the day level, \textcolor{red}{we don't use discounting} since the period of loan is only 90 days. \textcolor{red}{In robustness checks we do show that results are virtually unchanged when applying a wide range of time discounting factors.}

@@

As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year.\footnote{Loan term takes into account all the loan period, including those extended through refinancing}. The standard definition is given in the following formula:

@@

\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the behavioral literature on the ways to improve repayment in credit contracts, it enhances the regularity and salience of payments. It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers. The Commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement). The importance of this monthly payment was %reinforced in two ways; first by reminders issued to any borrower delinquent on the monthly payments that were supposed to be made, and secondly 
made salient in the contract and payment receipts (see Figure \ref{PaperSlip}), and by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments. The propose of the small fee was to mainly to make the structured schedule salient, not to be a large disincentive to be late. Transportation cost to go to the branch to pay is on the same order of magnitude as the fee in average.\footnote{The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable. In contrast with \cite{John} we don't let the clients choose the size of the fee. \cite{John} shows that doing this results in costly choices by (partially) naive present biased consumers. Our fee is much smaller than the median in her experiment. %We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.
} To elicit demand for the monthly payment contract, we include an arm that allows borrowers to opt into this contract if they choose. The existence of both a non-optional ``forcing'' arm, and a choice arm in our design is key to estimate a battery of treatment effects above an average treatment effect under fairly mild assumptions.

@@

%\todo[inline]{Somewhere in here we need to explain how we handle repeat pawns. If I recall correctly, we've settled on including only data for each person's first visit. This visit may include multiple pawns, but this is fine since we cluster at the branch-day level.}

@@

\paragraph{Timeline.} Figure \ref{exp_description}(a) \textcolor{red}{shows the timeline when the experiment happens and also the length of time for which we observe payments}. For contracts in the first week, we observe up to \hl{XXX} days, with \hl{XXX\%} of contracts ending during our sample period (in default or recovery). For contracts in the last week we observe up to \hl{XXX} days, and \hl{XXX\%} of contracts ending observed. Figure \ref{exp_description}(b) shows the number branch-days per arm, the number of contracts, and the number of surveys. %Not every contract has a survey for several reasons, we have survey information for \hl{XXX\%} of them. There were two reasons: \hl{XXX}.

@@

\paragraph{Attrition.} There are two main channels through which attrition could complicate the interpretation of our results. The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment they encounter in a given branch on the day they enter.  If this occurred it would introduce a self-selection dimension which would still reflect the overall impact of a treatment for the lender's portfolio but would no longer deliver \textit{ceteris paribus} effects of treatments on the same individual borrower.  Narrative reports and the way the treatment was implemented make us believe that this is unlikely.\footnote{Potential clients did not know that different days could have different contracts. If they asked, appraisers said that whatever was offered on that day was the only available contract for an undetermined length of time. Anecdotally, appraisers told us that they did not think refusals differed across arms, and our enumerators informed us that potential clients rarely left the branch without pawning. Lender P also never complained to us that our different treatments were hurting sales.} If the treatments had induced demand-side selection, we would expect to see that the number of pawns successfully conducted differ in a systematic way across arms.  To test for this, we examine the number of loans given per branch-day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day. The \hl{first} row of Table \ref{attrition_table} shows there is no difference between the Control and Forced Commitment arm in terms of the number of pawns per branch-day, suggesting that there has been no differential refusal.\footnote{The Choice arm appears to have a somewhat larger number of borrowers than the Control arm (p-value=\hl{XXX}), but we cannot reject equality with the Forced Commitment arm (p-value=\hl{XXX}), or across all arms (p-value=\hl{XXX}).}  Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.

@@

Two more subtle form of sample selection arise if the treatments induce borrowers to repawn in different ways (which they do), or to pay off loans at a different rate (which they do as well).  We pursue a simple approach to these problems, by using only the first experimental pawn taken by a given borrower during the study window (ignoring all subsequent loans), and by defining outcomes in a manner that is consistent whether or not the loan had been closed at the time that the study observation window ends (e.g., `loan was repaid', which is defined even if the loan had not been completed, versus `loan defaulted', which is not).  We return in the subsequent section to more detailed analysis of the implications of these two issues.

@@

\paragraph{Specification.} Table \ref{main_impact_table} presents estimates and standard errors from a standard pooled experimental regression 
\begin{equation} \label{basic_reg}
    y_{ij} = \alpha + \beta^F T_{i}^F + \beta^C T_{i}^C + \gamma X_{ij} + \epsilon_{ij}
\end{equation}
where $i$ indexes client, $j$ indexes branch, $T_{i}^F$ and $T_{i}^C$ are indicator variables for receiving the Forced or Choice arms, $X_{ij}$ are branch and day-of-week fixed effects. Standard errors are clustered at the branch-day level, the unit of treatment assignment\footnote{A minority of clients pawned on more than one day during the experiment. To avoid contamination from earlier treatments to which these individuals were exposed, we restrict our sample to each client's \emph{first visit}. Note that a client may pawn multiple items her first visit. We include these as separate observations. Because our standard errors are clustered at the branch-day level, they automatically account for any dependence in error terms arising from multiple pawns by the same client on her first visit.}.
The coefficients $\beta^F$ and $\beta^C$ are the ATEs of the forced commitment and choice treatments, respectively, on the outcome variable $y_{ij}$.\footnote{Note that $\beta^C$ can be viewed in two ways: as the the ATE of \emph{offering clients a choice} between the status quo and commitment contract or as the intent-to-treat effect of the commitment contract \emph{itself}. Here we adopt the former interpretation; below we use the latter to consider the relevance of selection-on-gains.}
Our two primary outcome variables are financial cost in pesos and Annual Percentage Rate (APR), as defined in Section \ref{costs}. 
Results for these outcomes appear in columns (1) and (6) of Table \ref{main_impact_table}.
The remaining columns decompose the financial cost and APR outcomes into their components: payments to capital, fees, interest, and the cost of losing the pawn. 
Columns (2)--(5) correspond to financial cost while columns (7)--(10) correspond to APR.

@@

As we explained above, loans can be extended for an additional 3 months by paying the interest owed and restarting the loan under the same treatment conditions. This means that some loans extend for more than 3 months. We consider the cost

\paragraph{Results.} The results are extremely stark.
The Forced Commitment arm yields large and significant decreases in the cost of loans to clients, as measured either by financial cost or APR. 
Despite causing an increase in payments to capital and fees, the Forced arm leads to a sharp decrease in overall costs of borrowing, driven by a XX percentage point decrease in the probability of default (more than a XX\% reduction from a baseline of XX\% default).  
A credit product that has an effective average APR of XXX\% in the status quo arm (inclusive of default) is reduced to a cost of XXX\% through the imposition of a more regularized payment structure.  
While the Forced arm increases fees significantly relative to a control mean of 0, the monetary value of the fees imposed is small (28 pesos).  
Payments towards capital also rise by XXX pesos because the arm is so effective at improving the fraction of individuals actually repaying their loans.  
Because the regular repayment structure moves the timing of payment forward it saves borrowers an average of 109 pesos in interest costs.  
The vast majority of the overall treatment effect, however, stems from the XXX pesos from not losing the pawn. 
In contrast, the Choice arm fails to deliver significant changes in any measure, with the exception of an increase in fees, for which we are highly powered since this outcome is zero for every control observation.

\paragraph{Intermediate outcomes.} To shed light on the mechanisms behind the ATEs discussed above, Table \ref{mechanisms} shows how treatment affects a number of intermediate outcomes. 
Column (1) shows that borrowers' first payment occurs 8 days earlier on average in the Forced Commitment arm than under the status quo.
Column 4 shows that the number of payments increases by 0.19.
Treatment effects are concentrated on the intensive margin, as treatment does \emph{not} affect the fraction of clients who fail to make any payments (Column 12). 
The percentage of the loan paid increases by 9 percentage points on average (Column 9). 
Moreover, the percentage of the loan paid is even smaller for those who end up losing the pawn (first row of column 9). 
This last point is critical. 
Forced commitment could be financially harmful if it caused individuals to make fruitless payments on loans for which they later defaulted. 
In contrast, we find that forced commitment causes individuals who would otherwise have made partial payments but ultimately defaulted to instead recover their pawn.

\todo[inline]{We need to add a bit of lead-in here to make clear why we're going all these robustness exercises. Basically we're trying to foreclose possible explanations for why the treatment could be harmful. We should say something here like ``when we say mistake below, what we mean by this is X and we're going to show you right now that explanations A, B, and C are not operative here.''}

\paragraph{Robustness.} We have shown that forcing borrowers to take the monthly payment contract significantly reduced financial cost. Although the paper focuses on financial cost, here we consider two additions to the cost and benefit calculation. We include the cost of going to the branch, and we consider the value of the pawn as perceived by the borrower instead of its gold value.

@@

@@

Because they identify both the ToT and TuT, \eqref{eq:ToTreg} and \eqref{eq:TuTreg} also identify the average selection on gains: $\text{ASG} = \text{ToT} - \text{TuT}$.
Carrying out inference for this quantity is a bit more involved, because $\text{ASG}$ a difference of coefficients from two separate IV regressions. 
In Appendix \hl{???} we show how to use the residuals from \eqref{eq:TuTreg} and \eqref{eq:ToTreg} to carry out cluster-robust inference for $\text{ASG}$. 
Our companion STATA package automates this procedure.
As mentioned above, the randomized choice design also identifies the average selection bias (ASB) and average selection on levels (ASL).
In particular,
\begin{align}
\label{eq:ASB}
    \text{ASB} &\equiv \mathbbm{E}(Y_{i0}|C_i=1) - \mathbbm{E}(Y_{i0}|C_i = 0) = \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0)}{\mathbbm{E}(D|Z=2)}\\
    \label{eq:ASL}
    \text{ASL} &\equiv \mathbbm{E}(Y_{i1}|C_i = 1) - \mathbbm{E}(Y_{i1}|C_i=0) = \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}
\end{align}
as we show in Appendix \hl{???}.
For purposes of inference, both the ASB and ASL can be re-written as the difference of coefficients from a pair of just-identified linear IV regressions, namely
\begin{align}
\label{eq:ASB0}
    \mathbbm{1}(Z_i\neq 1) (1 - D_i) Y_i &= \mathbbm{E}(Y_{i0}) \mathbbm{1}(Z_i = 0) + \mathbbm{E}(Y_{i0}|C_i=0)(1 - D_i)\mathbbm{1}(Z_i=2) + U_{i0}\\
\label{eq:ASB1}
    \mathbbm{1}(Z_i\neq 1) (1 - D_i) Y_i &= \mathbbm{E}(Y_{i0}) \mathbbm{1}(Z_i = 0) + \mathbbm{E}(Y_{i0}|C_i=1)(-D_i)\mathbbm{1}(Z_i = 2) + U_{i1}\\
\label{eq:ASL0}
    \mathbbm{1}(Z_i\neq 0) D_i Y_i &= \mathbbm{E}(Y_{i1}) \mathbbm{1}(Z_i = 1) + \mathbbm{E}(Y_{i1}|C_i=0)(D_i - 1)\mathbbm{1}(Z_i = 2) + V_{i0}\\
\label{eq:ASL1}
    \mathbbm{1}(Z_i\neq 0) D_i Y_i &= \mathbbm{E}(Y_{i1}) \mathbbm{1}(Z_i = 1) + \mathbbm{E}(Y_{i1}|C_i=1)D_i \mathbbm{1}(Z_i = 2) + V_{i1}
\end{align}
where the error terms $(U_{i0}, U_{i1})$ and $(V_{i0}, V_{i1})$ satisfy
\[
\mathbbm{E}
\begin{pmatrix}
V_{i0} \\ 
V_{i1} \\ 
\end{pmatrix} = 
\mathbbm{E}\begin{pmatrix}
U_{i0} \\ 
U_{i1} \\ 
\end{pmatrix}
= \mathbbm{E}\left[
\begin{pmatrix}
V_{i0} \\ 
V_{i1} \\ 
\end{pmatrix} \mathbbm{1}(Z_i = z)
\right]
= \mathbbm{E}\left[
\begin{pmatrix}
U_{i0} \\ 
U_{i1} \\ 
\end{pmatrix} \mathbbm{1}(Z_i = z)
\right] = 0
, \quad z = 0, 1, 2.
\]
As in the case of the ASG from above, inference for the ASB and ASL can be carried out by saving the residuals from \eqref{eq:ASB0}--\eqref{eq:ASL1}. 
These calculations are also automated in our companion STATA package.
For details, see Appendix \hl{???}.

\todo[inline]{Perhaps mention some other settings in which a design like this might be helpful? Need to hink about this.}

@@

\newpage
\begin{landscape}
\begin{table}[H]
\caption{Intermediate outcomes}
\label{mechanisms}
\begin{center}
\resizebox{1.45\textwidth}{!}{
\scriptsize{\input{./Tables/mechanism.tex}}
}
\end{center}

@@

\scriptsize {
\noindent This table explores treatment effects in ``intermediate variables''. Each column represents a different dependent variable following the main specification  (\ref{basic_reg}). The last row shows the mean of the dependent variable for the control group. Dependent variables are as follows: Column (1) shows the effect on the percentage of payments during the first visit. Column (2) records the probability of recovery in the first visit. Column (3) is the overall percentage of payment as fraction of the loan. Column (4) is the probability of making a positive payment and defaulting. Column (5) is the percentage of payments conditional on defaulting. Column (6) is the probability of ``selling'' the pawn, defined as not making any payment towards recovery of the item. Column (7) reports the probability of selling the pawn, conditional on defaulting. The bottom panel focuses on time related variables: Column (8) indicates the elapsed days toward the first payment. Column (9), (10), and (11) are related to the number of visits made to make payments, and columns (12), (13) speak on the loan duration.

In sum, we find that the Forced commitment contract clients pays 13.8 days earlier in average, during this first visit, clients pay 7.9\% more of the loan amount, with a 8\% increase probability of recovery. Moreover, the forced commitment contract reduces the probability of defaulting and making a positive payment by 7\%, thus another channel for savings is that treatment helps avoid making payments toward recovery but defaulting. 
However, we see no effect in the number of visits and the probability of selling the pawn.}

>>>>

We define a borrower's financial cost as the total monetary outflow --in cash or pawn value-- from the borrower to the lender. This includes all payments the borrower made toward interest and fees, but also the value of the pawn when there is default. When there is no default the borrower gets her pawn back and there is no loss of value for the borrower. Payments towards capital are considered a cost only when the borrower defaults, as she does not get reimbursed for these. Note however that when she does not default payments to capital are not an actual outflow, as they sum up to the value of the loan the lender disbursed in the first place. The formula for financial cost for person $i$ is thus as follows:

@@

\noindent where $t$ indexes days, and $\mathds{1}(\text{Default}_i)$ is an indicator function for defaulting. Because the period of the loan is only 90 days we do not use discounting in calculating costs.  In robustness checks we show that results are virtually unchanged when applying a wide range of time discounting factors.

@@

As a second measure of cost we calculate the Annual Percentage Rate (APR) in order to express the cost as a percentage of the loan, per year, inclusive of default costs.\footnote{Loan term takes into account all the loan period, including those extended through refinancing}. The standard definition is given in the following formula:

@@

\noindent \textbf{The Commitment Contract.} For the purpose of the experiment we designed a new contract that is identical to the status quo contract except that, informed by the designed of micro-lending contracts, it enhances the regularity and salience of payments as a way to encourage repayment \citep{morduch1999microfinance, bauer2012behavioral}.  It has the same interest rate (7\% \textit{per month}) which accumulates daily on outstanding debt, it has the same loan size/collateral ratio (70\%), it has the same loan term (90 days, and a grace period of 15 days), and the gold pawn gets appraised in the same way by the same appraisers. The Commitment contract however requires the client to make regular monthly payments for the duration of the contract, with the principal and interest payments split evenly across the three months of the contract (day 30, 60 and 90 after loan disbursement). The importance of this monthly payment was made salient in the contract and payment receipts (see Figure \ref{PaperSlip}), and by the levying of a nominal fee (2\% of minimum due) on individuals who fell behind in their payments. The propose of the small fee was to mainly to make the structured schedule salient, not to be a large disincentive to be late. Transportation cost to go to the branch to pay is on the same order of magnitude as the fee in average.\footnote{The lender was worried that if the fee was large, forgetting to pay could make the pawn unrecoverable. In contrast with \cite{John} we don't let the clients choose the size of the fee. \cite{John} shows that doing this results in costly choices by (partially) naive present biased consumers. Our fee is much smaller than the median in her experiment. %We also experimented with a contract where there was no pecuniary fee for paying late but where we clients made a personal promise to pay monthly.
} To elicit demand for the monthly payment contract, we include an arm that allows borrowers to opt into this contract if they choose. The existence of both a non-optional ``forcing'' arm, and a choice arm in our design is key to estimate a battery of treatment effects above an average treatment effect under fairly mild assumptions.

@@

@@

\paragraph{Timeline.} Figure \ref{exp_description}(a) shows the timeline when the experiment happens and also the length of time for which we observe payments. For contracts in the first week, we observe up to \hl{XXX} days, with \hl{XXX\%} of contracts ending during our sample period (in default or recovery). For contracts in the last week we observe up to \hl{XXX} days, and \hl{XXX\%} of contracts ending observed. Figure \ref{exp_description}(b) shows the number branch-days per arm, the number of contracts, and the number of surveys. %Not every contract has a survey for several reasons, we have survey information for \hl{XXX\%} of them. There were two reasons: \hl{XXX}.

@@

\paragraph{Attrition.} There are two main channels through which attrition could complicate the interpretation of our results. The first, and more serious, is the possibility that clients might change their pawning decisions in response to the treatment they encounter in a given branch on the day they enter.  If this occurred it would introduce a self-selection dimension which would still reflect the overall impact of a treatment for the lender's portfolio but would no longer deliver \textit{ceteris paribus} effects of treatments on the same individual borrower.  Narrative reports and the way the treatment was implemented make us believe that this is unlikely.\footnote{Potential clients did not know that different days could have different contracts. If they asked, appraisers said that whatever was offered on that day was the only available contract for an undetermined length of time. Anecdotally, appraisers told us that they did not think refusals differed across arms, and our enumerators informed us that potential clients rarely left the branch without pawning. Lender P also never complained to us that our different treatments were hurting sales.} If the treatments had induced demand-side selection, we would expect to see that the number of pawns successfully conducted differ in a systematic way across arms.  To test for this, we examine the number of loans given per branch-day, with specific attention to whether the Forced Commitment arm led to a lower number of borrowers per day. The \hl{first} row of Table \ref{attrition_table} shows there is no difference between the Control and Forced Commitment arm in terms of the number of pawns per branch-day.\footnote{The Choice arm appears to have a somewhat larger number of borrowers than the Control arm (p-value=\hl{XXX}), but we cannot reject equality with the Forced Commitment arm (p-value=\hl{XXX}), or across all arms (p-value=\hl{XXX}).}  The second row makes the same point in a more focused way, given that the surveys were conducted prior to the revelation of treatment status.  In no arm did more than three percent of individuals refuse loans subsequent to the survey, and neither these rates nor the rate of survey response are different across arms.  Therefore it appears that the treatments have not induced any endogenous shifts in the composition of borrowers.

@@

A more subtle form of sample selection could arise if the treatments induce borrowers to re-pawn in different ways, especially given that their treatment status on subsequent loan/days may not be the same as that initially assigned.  To handle this issue our analysis uses only the first loan taken by each individual during the experimental window.

@@

\paragraph{Specification.} Table \ref{main_impact_table} presents estimates and standard errors from a standard pooled experimental regression 
\begin{equation} \label{basic_reg}
    y_{ij} = \alpha + \beta^F T_{i}^F + \beta^C T_{i}^C + \gamma X_{ij} + \epsilon_{ij}
\end{equation}
where $i$ indexes client, $j$ indexes branch, $T_{i}^F$ and $T_{i}^C$ are indicator variables for receiving the Forced or Choice arms, $X_{ij}$ are branch and day-of-week fixed effects. Standard errors are clustered at the branch-day level, the unit of treatment assignment\footnote{A minority of clients pawned on more than one day during the experiment. To avoid contamination from earlier treatments to which these individuals were exposed, we restrict our sample to each client's \emph{first visit}. Note that a client may pawn multiple items her first visit. We include these as separate observations. Because our standard errors are clustered at the branch-day level, they automatically account for any dependence in error terms arising from multiple pawns by the same client on her first visit.}.
The coefficients $\beta^F$ and $\beta^C$ are the ATEs of the forced commitment and choice treatments, respectively, on the outcome variable $y_{ij}$.\footnote{Note that $\beta^C$ can be viewed in two ways: as the the ATE of \emph{offering clients a choice} between the status quo and commitment contract or as the intent-to-treat effect of the commitment contract \emph{itself}. Here we adopt the former interpretation; below we use the latter to consider the relevance of selection-on-gains.}
Our two primary outcome variables are financial cost in pesos and Annual Percentage Rate (APR), as defined in Section \ref{costs}. 
Results for these outcomes appear in columns (1) and (6) of Table \ref{main_impact_table}.
The remaining columns decompose the financial cost and APR outcomes into their components: interest payments (col 2), payment towards any fees incurred (col 3), payments toward the principal (col 4). It is of interest to this research and to Lender P whether structured frequent payment decrease default. In column 6 the dependent variable is a dummy indicating default. Column 5 shows the value of lost pawn conditional on losing it. Finally, column 7 rescales financial cost as a function of loan size to estimate causal effects on incurred APR.\footnote{As we explained above, loans can be extended for an additional 3 months by paying the interest owed and restarting the loan under the same treatment conditions. This means that some loans extend for more than 3 months. We consider the entire flow of cost from the duration of our sample.}

@@

\paragraph{Results.} The results are stark. The Forced Commitment arm yields large and significant decreases in the cost of loans to clients, as measured either by financial cost or APR. Despite causing an increase in fees, the Forced arm leads to a decrease of 379 pesos in the costs of borrowing (out of a group mean of 1851 in the status quo), that is equivalent to 20\% reduction as a fraction of mean cost. These cost savings arise from a 6.5 percentage point (pp) decrease in the probability of default (out of a baseline mean of 44pp), which implies cost savings of 254 pesos. But also from lower interest payments, since as we will document the treatment is effective at speeding up payments, with the benefits that the interest rate applies to a smaller principal. This translates into a large reduction in APR. A credit product that has an effective average APR of 184\% in the status quo arm (inclusive of default) is reduced to a cost of 34\% through the imposition of a more regularized payment structure.

In contrast, to the impressive effectiveness of the Forced commitment arm, the Choice arm fails to deliver significant changes in any measure, with the exception of an increase in fees, for which we are highly powered since this outcome is zero for every control observation. Giving borrowers the choice of contract did not decrease financial cost, whereas forcing them into a structured payment contract dramatically reduced it. As we explore later in the paper, the null effect of the Choice arm arises because few people had demand for it, with \hl{XXX\%} choosing the less effective status-quo contract.

\paragraph{Intermediate outcomes.} To shed light on the mechanisms behind the ATEs discussed above, Table \ref{mechanisms} shows how treatment affects a number of intermediate outcomes. One can group the types of intermediate outcomes into two categories: measures of the speed of pawn recovery, and measures of the decision of when to default. While the first payment for borrowers in the status-quo contract occurs on average only on day 82 (on a 90 days contract), borrowers in the forced commitment arm start paying 13.8 days earlier on average (col 1). Not only do they start paying earlier, the first payment is also 7.9\% larger (col 2), and a larger fraction of 7.9\% actually pay in full and recover their pawn in the first payment , compared to 30\% in the status quo contract (col 3). The resolution of the loan (either by payment or default) is shortened by 27.9 days (col 4), and conditional on recovery (an endogenous control) by 17.9 days (col 5).

A very undesirable outcome from the borrower's perspective is to pay towards the loan without paying in full, i.e. defaulting on the loan. In this case, they lose both the collateral and any payments made toward recovery. One could be concerned that by encouraging them to pay monthly, more borrowers could end up in this dire scenario in the Forced commitment contract. Column 6 shows this is not the case. On the contrary,  7 percentage points fewer borrowers end up in this situation, compared to 12 percent in the status quo contract. Conditional on defaulting those assigned to the Force commitment contract have paid 3.9\% less of their loan (col 7), and 14 percentage higher proportion of borrowers pay zero conditional on defaulting, an outcome analogous to selling their pawn (col 8). One interpretation of these results is that the Forced commitment contract forces borrowers to think earlier about whether they will indeed be able to eventually recover their pawn, and separates borrowers into those ``selling'' their pawn and those recovering it, reducing the share of undecided borrowers that end up paying interest and end up losing the pawn anyway. This mechanism may also help to explain why the Forced commitment contract does not increase the number of visits to the branch to pay (col 9): those recovering their pawn visit more, but those defaulting have 0.19 less visits (col 10).

\paragraph{Other costs.} We have shown that forcing borrowers to take the monthly payment contract significantly reduces financial cost. Although the paper focuses on financial cost, we consider three additional costs here. First, We include the cost of going to the branch. This includes the self-reported transport cost (most use public transport), as well as the opportunity cost of time. To err on the conservative side, we subtract a whole day's minimum wage the day of the visit, instead of just the wage corresponding to a couple of hours. Second, we consider a rough proxy of the value of liquidity they lose by paying earlier. We act as if each payment they make comes from an additional loan they take, which incurs interest at the same rate as Lender P's loan (7\% per month). So far we have valued the collateral at the gold value appraised by the lender, but the piece may be worth more to the borrower than its gold value. 
For many of them the pawned jewelry has sentimental value as well. This is reflected in the subjective valuation they reported in the survey\footnote{The minimum peso amount at which they would sell the piece.} which is \hl{XXX\%} higher on average. Our third extra cost considers this higher value.

Table \ref{table_robustness_fc} shows results. We present results

@@

\subsection{Censoring of Loan Completion}

The window of time during which we were able to observe borrower behavior was limited in each branch, meaning that there were loans that we do not see completed (particularly those pawns that were rolled over for one or two further 90-day spells).  Overall, XX\% of all experimental loans are censored, meaning that they neither default nor repay within the observation window.  In the prior analysis we handle this issue by using outcomes such as `did not default' which are defined even when we do not observe the completion of the loan, and only considering costs that we observe directly.  We have also showed, however, that one effect of the forcing arm is to accelerate repayment, meaning that it is less likely for loans in this arm to be censored.  This issue is illustrated in Figure \ref{survival_graph}, which shows the CDF of loan completion (Panel (a)) and loan recovery (Panel (b)) by the number of days since first pawn.  Two features of these graphs are salient for our analysis.  The first is the extent to which loan outcomes are observed more quickly in the forcing arm.  This is primarily due to the the substantially higher rate of repayment of Forced Commitment loans at 120 days (~15 pp higher than the other arms).  The second is the very low rate at which loans are recovered in any arm after 120 days.  In the 180 day window after the second rollover period we see a further ~10 percent of loans repaid in all arms, but these loans are largely dormant, suggesting that many of the censored loans will in fact be defaulted upon.

The confluence of censoring and a treatment effect on censoring is problematic from an experimental point of view.  The approach taken so far is a conservative one in that it inherently assumes that all of the loans outstanding at the end of the observation window will be repaid, making it so that the acceleration of payment observed in the Forced arm does not translate mechanically into a treatment effect on default.  Given the centrality of this issue to the observed costs, we now delve into it more detail.  One way of considering the effect that this issue could have on our results is to make extreme assumptions about the outcome of these loans in the treatment and control so as to bound the possible influence of censoring.  In Table \ref{mns} we compare the Forced and Control arms, making the bracketing assumptions about repayment on censored loans.  Panel A assumes all censored loans are repaid, and Panel D that all default.  Panel B provides the lower bound for the treatment effect by assuming censored control loans are always repaid and treatment loans never are, and Panel C the upper bound by making the reverse assumption.  Comfortingly, even with these extreme assumptions the significance on the main treatment effects never flips and treatment effects on financial cost and interests payments remain negative and significant in all scenarios.  So there appears to be no scope for the censoring issue to overturn our main results.

Finally, Panel E of this table conducts a logit prediction model that uses all of the available information on loans that were completed to predict the outcome of loans that were not.  This is a best guess of the outcome on censored loans.  Using this prediction, we replicate the main experimental results and find that the treatment effect on financial cost increases from -378 (main results) to -525 (censored loans predicted), and the APR from -34\% to -62\%.  Hence, while the censoring issue does have a substantial influence on the magnitude of our estimated treatment effects, these  checks confirm that a) the core results are robust to censoring, and b) the headline approach that we take to the issue is conservative and is likely understating the true magnitude of impacts.

@@

Because they identify both the ToT and TuT, \eqref{eq:ToTreg} and \eqref{eq:TuTreg} also identify the average selection on gains: $\text{ASG} = \text{ToT} - \text{TuT}$.
Carrying out inference for this quantity is a bit more involved, because $\text{ASG}$ a difference of coefficients from two separate IV regressions. 
In Appendix \hl{???} we show how to use the residuals from \eqref{eq:TuTreg} and \eqref{eq:ToTreg} to carry out cluster-robust inference for $\text{ASG}$. 
Our companion STATA package automates this procedure.
As mentioned above, the randomized choice design also identifies the average selection bias (ASB) and average selection on levels (ASL).
In particular,
\begin{align}
\label{eq:ASB}
    \text{ASB} &\equiv \mathbbm{E}(Y_{i0}|C_i=1) - \mathbbm{E}(Y_{i0}|C_i = 0) = \frac{\mathbbm{E}(Y|Z=0) - \mathbbm{E}(Y|Z=2,D=0)}{\mathbbm{E}(D|Z=2)}\\
    \label{eq:ASL}
    \text{ASL} &\equiv \mathbbm{E}(Y_{i1}|C_i = 1) - \mathbbm{E}(Y_{i1}|C_i=0) = \frac{\mathbbm{E}(Y|Z=2,D=1) - \mathbbm{E}(Y|Z=1)}{1 - \mathbbm{E}(D|Z=2)}
\end{align}
as we show in Appendix \hl{???}.
For purposes of inference, both the ASB and ASL can be re-written as the difference of coefficients from a pair of just-identified linear IV regressions, namely
\begin{align}
\label{eq:ASB0}
    \mathbbm{1}(Z_i\neq 1) (1 - D_i) Y_i &= \mathbbm{E}(Y_{i0}) \mathbbm{1}(Z_i = 0) + \mathbbm{E}(Y_{i0}|C_i=0)(1 - D_i)\mathbbm{1}(Z_i=2) + U_{i0}\\
\label{eq:ASB1}
    \mathbbm{1}(Z_i\neq 1) (1 - D_i) Y_i &= \mathbbm{E}(Y_{i0}) \mathbbm{1}(Z_i \neq 1) + \mathbbm{E}(Y_{i0}|C_i=1)(-D_i)\mathbbm{1}(Z_i = 2) + U_{i1}\\
\label{eq:ASL0}
    \mathbbm{1}(Z_i\neq 0) D_i Y_i &= \mathbbm{E}(Y_{i1}) \mathbbm{1}(Z_i \neq 0) + \mathbbm{E}(Y_{i1}|C_i=0)(D_i - 1)\mathbbm{1}(Z_i = 2) + V_{i0}\\
\label{eq:ASL1}
    \mathbbm{1}(Z_i\neq 0) D_i Y_i &= \mathbbm{E}(Y_{i1}) \mathbbm{1}(Z_i = 1) + \mathbbm{E}(Y_{i1}|C_i=1)D_i \mathbbm{1}(Z_i = 2) + V_{i1}
\end{align}
where the error terms $(U_{i0}, U_{i1})$ and $(V_{i0}, V_{i1})$ satisfy
\[
\mathbbm{E}
\begin{pmatrix}
V_{i0} \\ 
V_{i1} \\ 
\end{pmatrix} = 
\mathbbm{E}\begin{pmatrix}
U_{i0} \\ 
U_{i1} \\ 
\end{pmatrix}
= \mathbbm{E}\left[
\begin{pmatrix}
V_{i0} \\ 
V_{i1} \\ 
\end{pmatrix} \mathbbm{1}(Z_i = z)
\right]
= \mathbbm{E}\left[
\begin{pmatrix}
U_{i0} \\ 
U_{i1} \\ 
\end{pmatrix} \mathbbm{1}(Z_i = z)
\right] = 0
, \quad z = 0, 1, 2.
\]
As in the case of the ASG from above, inference for the ASB and ASL can be carried out by saving the residuals from \eqref{eq:ASB0}--\eqref{eq:ASL1}. 
These calculations are also automated in our companion STATA package.
For details, see Appendix \hl{???}.

\todo[inline]{Perhaps mention some other settings in which a design like this might be helpful? Need to think about this.}

@@

\newpage
\begin{landscape}
\begin{table}[H]
\caption{Intermediate outcomes}
\label{mechanisms}
\begin{center}
\resizebox{1.30\textwidth}{!}{
\scriptsize{\input{./Tables/mechanism.tex}}
}
\end{center}

@@

\scriptsize {
\noindent This table explores treatment effects in ``intermediate variables''. Each column represents a different dependent variable following the main specification  (\ref{basic_reg}). The last row shows the mean of the dependent variable for the control group. Panel A talks about the speed of payment. Column (1) indicates the elapsed days toward the first payment. Column (2) shows the effect on the percentage of payments during the first visit. Column (3) records the probability of recovery in the first visit, and columns (4), (5) speak on the loan duration. Panel B are variables related to default. Column (6) is the probability of making a positive payment and defaulting. Column (7) is the percentage of payments conditional on defaulting.  Column (8) reports the probability of selling the pawn, conditional on defaulting. Finally Panel C is related to the number of visits made to make payments.

In sum, we find that the Forced commitment contract clients pays 13.8 days earlier in average, during this first visit, clients pay 7.7\% more of the loan amount, with a 8\% increase probability of recovery. Moreover, the forced commitment contract reduces the probability of defaulting and making a positive payment by 7\%, thus another channel for savings is that treatment helps avoid making payments toward recovery but defaulting.}
